---
title: "Always check data"
author: "Ana Martinovici"
date: "Last compiled on `r Sys.Date()`"
output: 
    bookdown::html_document2:
        toc: true
        toc_float: 
            collapsed: false
        number_sections: true
        code_folding: hide
        theme: cerulean
editor_options: 
  chunk_output_type: console
---


```{r load-data}
library("tidyverse")
load("examples/recent_search/processed_data.RData")
```

# Data descriptives

# Location info in tweets

Let's see which of the tweets, if any have location info. We have `r nrow(df_tweets)` and `r nrow(df_tweets %>% filter(geo_place_id != "no_geo_info"))` have location info.

```{r data-checks-location}
# tweets with location info
df_tweets %>% 
	filter(geo_place_id != "no_geo_info") %>% 
	select(text, 
		   geo_place_id)

# add the name of that location
df_tweets <- df_tweets %>% 
	left_join(df_places, by = c("geo_place_id" = "place_id"))
df_tweets %>% 
	filter(geo_place_id != "no_geo_info") %>% 
	select(text, 
		   geo_place_id, 
		   place_full_name,
		   place_name)

df_ref_tweets <- df_ref_tweets %>% 
	left_join(df_places, by = c("ref_geo_place_id" = "place_id"))
df_ref_tweets %>% 
	filter(ref_geo_place_id != "no_geo_info") %>% 
	select(ref_text, 
		   ref_geo_place_id, 
		   place_full_name,
		   place_name)

```

# Length of tweet text

Adding the length of the tweet text and checking if there are differences between different types of tweets. Check duplicate entries for tweets and referenced tweets and figure out where they are coming from.

```{r length-of-text-1}
df_tweets <- df_tweets %>% 
	mutate(text_length = str_length(text))
df_tweets %>% 
	group_by(tweet_type) %>% 
	summarise(max_length = max(text_length))

df_ref_tweets <- df_ref_tweets %>% 
	mutate(ref_text_length = str_length(ref_text))

nrow(distinct(df_tweets %>% select(tweet_id)))
nrow(distinct(df_tweets %>% select(ref_tweet_id)))
nrow(distinct(df_ref_tweets %>% select(ref_tweet_id)))

df_tweets <- df_tweets %>% 
	left_join(df_ref_tweets %>% 
			  	select(ref_tweet_id, ref_text, ref_text_length),
			  by = "ref_tweet_id")
df_tweets %>% 
	group_by(tweet_type) %>% 
	summarise(max_length = max(text_length),
			  max_ref_length = max(ref_text_length))

df_tweets %>% 
	filter(tweet_type == "retweeted", ref_text_length > 150) %>%
	select(tweet_id, text, text_length, ref_tweet_id, ref_text, ref_text_length)
```

The **text** in **df_tweets** is truncated for retweets. If you want to use the full text of the tweet that was retweeted, then you need to use **ref_text**.

```{r length-of-text-2}

df_tweets %>% 
	filter(tweet_type == "retweeted") %>%
	ggplot(aes(x = ref_text_length, y = text_length)) +
	geom_point(col = "blue", size = 2) +
	geom_abline(intercept = 0, slope = 1) +
	theme_bw() +
	xlab(label = "Number of characters in the original tweet") +
	ylab(label = "Number of characters in the RT") +
	scale_x_continuous(limits = c(0, 320)) +
	scale_y_continuous(limits = c(0, 160)) +
	coord_fixed(ratio = 1)

```

# Public metrics

## Retweet count

Adding metrics of referenced tweets. 

```{r public-metrics-1}
df_tweets <- df_tweets %>% 
	left_join(df_ref_tweets %>% select(ref_tweet_id, 
									   ref_retweet_count, ref_reply_count,
									   ref_like_count, ref_quote_count),
			  by = "ref_tweet_id")
```

Let **Tweet 1** be the id of an "original tweet". Then, if this original tweet gets retweeted, let the id of the RT be **Tweet 2**. The retweet count associated with **Tweet 2** is the same as that associated with **Tweet 1**. The figure below show this for our sample:

```{r retweets-1}
df_tweets %>% 
	filter(tweet_type == "retweeted") %>% 
	ggplot(aes(x = retweet_count, y = ref_retweet_count)) +
	geom_point(size = 2, col = "blue") +
	geom_abline(intercept = 0, slope = 1) +
	theme_bw() +
	xlab(label = "Retweet count in df_tweets") +
	ylab(label = "Retweet count in df_ref_tweets")

```

This is different for quoted tweets. Let **Tweet 3** be a quoted tweet, starting from **Tweet 1**. Then, the retweet count associated with **Tweet 3** gives the number of times that **Tweet 3** was retweeted.

```{r retweets-2}

df_labels <- c("replied_to" = paste("Replied_to (n = ", 
									nrow(df_tweets %>% filter(tweet_type %in% c("replied_to"))), ")", sep = ""),
			   "quoted" = paste("Quoted (n = ", 
			   				 nrow(df_tweets %>% filter(tweet_type %in% c("quoted"))), ")", sep = ""),
			   "retweeted" = paste("Retweeted (n = ", 
			   					nrow(df_tweets %>% filter(tweet_type %in% c("retweeted"))), ")", sep = ""))

df_tweets %>% 
	filter(tweet_type %in% c("replied_to", "quoted", "retweeted")) %>% 
	ggplot(aes(x = retweet_count, y = ref_retweet_count)) +
	geom_point(size = 2) +
	facet_grid(cols = vars(tweet_type), 
			   scales = "free",
			   labeller = labeller(tweet_type = df_labels)) +
	theme_bw() +
	xlab(label = "Retweet count in df_tweets") +
	ylab(label = "Retweet count in df_ref_tweets")

```

## Quote retweets


```{r quote-1}
df_tweets %>% 
	filter(tweet_type %in% c("quoted", "retweeted")) %>% 
	ggplot(aes(x = quote_count, y = ref_quote_count)) +
	geom_point(size = 2) +
	facet_wrap(vars(tweet_type)) +
	theme_bw() +
	xlab(label = "Quote count in df_tweets") +
	ylab(label = "Quote count in df_ref_tweets")

```


## Likes

Looks like tweets that are retweeted also get quite a few likes. And those likes count towards the original tweet.

```{r likes-1}
df_tweets %>% 
	filter(tweet_type %in% c("quoted", "retweeted")) %>% 
	ggplot(aes(x = like_count, y = ref_like_count)) +
	geom_point(size = 2) +
	facet_wrap(vars(tweet_type),
			   scales = "free") +
	theme_bw() +
	xlab(label = "Like count in df_tweets") +
	ylab(label = "Like count in df_ref_tweets")

```

## Replies

```{r replies-1}
df_tweets %>% 
	filter(tweet_type %in% c("quoted", "retweeted")) %>% 
	ggplot(aes(x = reply_count, y = ref_reply_count)) +
	geom_point(size = 2) +
	facet_wrap(vars(tweet_type),
			   scales = "free") +
	theme_bw() +
	xlab(label = "Reply count in df_tweets") +
	ylab(label = "Reply count in df_ref_tweets")

```